Effects of CHILDREN's programs

### 2020-02-27 paper.Rnw

In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet. Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all, most, some, few, and none. For this figure, we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Health outcome over time}
  \label{Health_timeplots}
<<HealthTimePlots, echo=FALSE, message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none.}
\end{figure}

In Figure \ref{Health_timeplots}, for the variable 'lessIll_ordered', there is much non available data (lessIll_ordered refers to the share of beneficiaries who are less frequently ill). In all years, most organizations say that most beneficiaries are more healthy. The least stated category is, that all beneficiaries are less ill. That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll_ordered', appears as good as never.

In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet. The least stated category is that some beneficiaries increased their dietary knowledge. The leftover category, few, does not appear.

The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet). Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet. The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet. The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet. The leftover category, few, also does not appear.

@@

\begin{figure}
  \caption{Selfworth and everyday expertise over time}
  \label{Equality_timeplots}
<<EqualityTimePlots, echo=FALSE, message=FALSE>>=
Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
print(Equality_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN has always asked about following two variables. These are the shares of beneficiaries with improved self-worth (selfworth\_ordered) and with a broadened understanding for everyday expertise (dayToDaySkills\_ordered).
The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none.}
\end{figure}

Figure \ref{Equality_timeplots} shows in its upper plot the development of the answered categories for the variable selfworth_ordered (refers to the share of beneficiaries with improved self-worth). Mostly, the answer is that most beneficiaries in most organizations have more selfworth. The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth. The leftover category, few, does not appear.

In the bottom plot of figure \ref{Equality_timeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible. The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.

@@

texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE)

@@

texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE)
@

@@

Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables. For these results, we use their ordinal values. The x-axis displays the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none. For example, if an organization says that most beneficiaries are healthier, then this would be coded as most. In the last reporting period, there are 13 healthy diet criteria. In previous years there were up to 15. The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not. The healthy food incex is calculated as the number of fulfilled criteria. Examples for criteria are daily carbohydrates or daily vegetables.

All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria. The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet. It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy. However, for the variable less ill, the least data is availabe. Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables. This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.

\begin{figure}
  \caption{Health Outcomes versus Healthy Meals}
  \label{Health_Plots}
<<HealthRegressionsPercentageplots, echo=FALSE, message=FALSE>>=
Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
print(Health_percentageplots)
@
\floatfoot{DGECriteriaNo is an index of healthy diet criteria fulfilled in organization's menu. It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). According to information from CHILDREN, they ask the organizations to send them a sample of their menus. An ecotrophologist collaborating with CHILDREN assessed the menus. In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few, and none}
\end{figure}

@@

where \begin{itshape}{i}\end{itshape} indexes the identification number of each organization supported by CHILDREN and \begin{itshape}{t}\end{itshape} indexes the year of observation. The outcome variable, denoted by \begin{itshape}Y_{it}\end{itshape}, is either selfworth or everyday expertise. As mentioned in the previous section, \begin{itshape}TreatEF_{it}\end{itshape} represents the treatment status of organization \begin{itshape}{i}\end{itshape} in year \begin{itshape}{t}\end{itshape}. The corresponding regression coefficient \begin{itshape}\beta\end{itshape} represents the DiD estimator, which measures the average treatment effect of participating in the trips program.

The panel data set allows us to implement fixed effects. In our analysis we introduce individual fixed effects and time fixed effects. The ID fixed effects \begin{itshape}\gamma_{i}\end{itshape} control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions. For example, the state of an organization does not vary over time but might differ across supported social institutions. Additionally, the year fixed effects \begin{itshape}\delta_{t}\end{itshape} capture all variables that change across years but are the same for all organizations and within a specific year. For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.

>>>>

In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet. Figure \ref{HealthTimeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all, most, some, few, and none. For this figure, we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Health outcome over time}
  \label{HealthTimeplots}
<<HealthTimePlots, echo=FALSE, message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none.}
\end{figure}

In Figure \ref{HealthTimeplots}, for the variable 'lessIll\_ordered', there is much non available data (lessIll\_ordered refers to the share of beneficiaries who are less frequently ill). In all years, most organizations say that most beneficiaries are more healthy. The least stated category is, that all beneficiaries are less ill. That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll\_ordered', appears as good as never.

In the second plot of figure \ref{HealthTimeplots} (variable 'dietaryKnowledge\_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet. The least stated category is that some beneficiaries increased their dietary knowledge. The leftover category, few, does not appear.

The the bottom plot of figure \ref{HealthTimeplots}, which visualizes the variable 'appreciateHealthy\_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet). Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet. The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet. The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet. The leftover category, few, also does not appear.

@@

\begin{figure}
  \caption{Selfworth and everyday expertise over time}
  \label{EqualityTimeplots}
<<EqualityTimePlots, echo=FALSE, message=FALSE>>=
Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
print(Equality_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN has always asked about following two variables. These are the shares of beneficiaries with improved self-worth (selfworth\_ordered) and with a broadened understanding for everyday expertise (dayToDaySkills\_ordered).
The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none.}
\end{figure}

Figure \ref{EqualityTimeplots} shows in its upper plot the development of the answered categories for the variable selfworth\_ordered (refers to the share of beneficiaries with improved self-worth). Mostly, the answer is that most beneficiaries in most organizations have more selfworth. The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth. The leftover category, few, does not appear.

In the bottom plot of figure \ref{EqualityTimeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible. The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.

@@

texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)

@@

texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE, use.packages=FALSE)
@

@@

Figure \ref{HealthPlots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables. For these results, we use their ordinal values. The x-axis displays the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none. For example, if an organization says that most beneficiaries are healthier, then this would be coded as most. In the last reporting period, there are 13 healthy diet criteria. In previous years there were up to 15. The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not. The healthy food incex is calculated as the number of fulfilled criteria. Examples for criteria are daily carbohydrates or daily vegetables.

All plots of Figure \ref{HealthPlots} show that most organizations suffice about 5 to 10 healthy food criteria. The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet. It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy. However, for the variable less ill, the least data is availabe. Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables. This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.

\begin{figure}
  \caption{Health Outcomes versus Healthy Meals}
  \label{HealthPlots}
<<HealthRegressionsPercentageplots, echo=FALSE, message=FALSE>>=
Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
print(Health_percentageplots)
@
\floatfoot{DGECriteriaNo is an index of healthy diet criteria fulfilled in organization's menu. It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). According to information from CHILDREN, they ask the organizations to send them a sample of their menus. An ecotrophologist collaborating with CHILDREN assessed the menus. In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few, and none}
\end{figure}

@@

where $i$ indexes the identification number of each organization supported by CHILDREN and $t$ indexes the year of observation. The outcome variable, denoted by $Y_{it}$, is either selfworth or everyday expertise. As mentioned in the previous section, $TreatEF_{it}$ represents the treatment status of organization $i$ in year $t$. The corresponding regression coefficient $\beta$ represents the DiD estimator, which measures the average treatment effect of participating in the trips program.

The panel data set allows us to implement fixed effects. In our analysis we introduce individual fixed effects and time fixed effects. The ID fixed effects $\gamma_{i}$ control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions. For example, the state of an organization does not vary over time but might differ across supported social institutions. Additionally, the year fixed effects $\delta_{t}$ capture all variables that change across years but are the same for all organizations and within a specific year. For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.
